PanGraph: scalable bacterial pan-genome graph construction

### 2022-09-13 main.tex
feat: updated panx benchmark figs
feat: caption of real data benchmark

\begin{figure*}[htb]
    \includegraphics[width=.7\textwidth]{figs/panx_benchmark.pdf}
    \caption{{\bf Benchmark on real data}.}
    \label{fig:panx-benchmark}
\end{figure*}

>>>>

% TODO: talk more extensively about the meaning of the results?
\begin{figure*}[htb]
    \includegraphics[width=\textwidth]{figs/panx_benchmark.pdf}
    \caption{{\bf Benchmark on real data}.
        We build pangenome graphs from fully-assembled chromosomes from 5 different bacterial species. For each species we build graphs with three different alignment kernel options (\textit{minimap2} with \textit{asm10} or \textit{asm20} option and \textit{mmseqs2}) and two different settings for the pseudo-energy parameters (standard or null values).
        \textbf{A}: \textit{PanGraph} wall-time when run in parallel on 8 cores.
        \textbf{B}: fraction of core pangenome in the pangenome graph.
        \textbf{C}: sequence compression, measured as the ratio between the pangenome graph size and the cumulative size of all the sequences contained in the graph.
    }
    \label{fig:panx-benchmark}
\end{figure*}
